GO

### 2020-03-28 analysis/12_GO.Rmd
candidate genes slim

```{r}
candidates <- c("OXT", "AVP", "GNRH1", "GNRHR", 
                    "AR", "POMC", "AGRP", 
                       "CRH", "AVPR1A", "AVPR1B", "AVPR2","VIP",
                       "CYP19A1", "DRD1", "DRD2", "PRL", "PRLR", "SOX9", 
                    "ESR1","ESR2", "LBH", "CDK1", "BRCA1",
                    "PTEN", "CREBBP", "FOS", "JUN", "EGR1",
                     "BDNF", "GRM2","GRIA1",
                    "KCNJ5", "CISH", "PTGER3", "CEBPD", "ZBTB16", 
                    "DIO3", "DIO2", "DIO1",

                     "VIPR1", "VIPR2", "NPY", "LH", "FSH", "FSHB",
                    "JAK2", "HCRT", "TRH", "TSHB",
                    "MC3R", "MC4R", "MC5R",  "NR3C1", "NR3C2",
                    "STAT5B","NPVF")

@@

row.names(candidate_DEGs) <- candidate_DEGs$GO  
candidate_DEGs <- t(candidate_DEGs)
candidate_DEGs <- as.data.frame(candidate_DEGs)
kable(candidate_DEGs)

bioprocshinyGO <- c("topBiologicalProcessGO",
                    "Prostate gland growth",
                    "Cellular response to hormone stimulus",
                    "Response to endogenous stimulus",
                    "Mammary gland development",
                    "Response to hormone",
                    "Response to endogenous stimulus",
                    NA,
                    "Regulation of animal organ morphogenesis",
                    "Temperature homeostasis",
                    "Prostate gland growth",
                    NA,NA,NA,
                    "Cellular response to hormone stimulus",
                    NA,
                    "Regulation of cell communication",
                    NA,
                    "Cell-cell signaling",
                    "Cellular response to hormone stimulus",
                    "Positive regulation of ossification",
                    "G2 DNA damage checkpoint"
                    )

candidate_DEGs <- cbind(candidate_DEGs, bioprocshinyGO)
kable(candidate_DEGs)

>>>>

```{r}

candidategenesslim <- c("OXT", "AVP", "GNRH1", "GNRHR", 
                    "AR",  "CYP19A1", 
                     "AVPR1A", "AVPR1B", "AVPR2","VIP",
                  "DRD1", "DRD2", 
                  "PRL", "PRLR",  
                    "ESR1","ESR2", "LBH",

                    "FOS", "JUN", "EGR1", "BDNF"
                      )

candidates <- candidategenesslim

@@

row.names(candidate_DEGs) <- candidate_DEGs$GO  
candidate_DEGs <- t(candidate_DEGs)
candidate_DEGs <- as.data.frame(candidate_DEGs)
kable(candidate_DEGs) 
```
